# Quarto examples

## Equations 

Here's an equation: 

$$ 
\frac{\mathrm{d}N}{\mathrm{d}t} = rN(1 - \frac{N}{K}) 
$$ {#eq-log}

And @eq-log is a reference to the equation above. 

## References

See @knuth84 for additional discussion of literate programming.

## Syntax highlighting

Here's some python code: 

```python
import numpy as np
np.random.seed(42)
a = 1 + 2
b = a + 3
print("Hello")
```

## Visualising data (R)

Here's an interactive plot generated with R:

```{r}
#| echo: false
#| eval: true
#| warning: false
library(ggplot2)
library(plotly)
library(dplyr)
data <- data.frame(
  x = c(1, 5, 3, 4, 5),
  y = c(1, 2, 2, 4.1, 10)
)

myplot <- data %>% ggplot(aes(x=x,y=y)) +
  geom_point() +
  geom_line() +
  labs(title = "My Plot", x = "X-axis", y = "Y-axis") +
  theme_minimal()

ggplotly(myplot)
```

## A youtube clip:

{{< video https://www.youtube.com/embed/wo9vZccmqwc >}}

## An 'iframe' to a different page (e.g. my simulations)


```{=html}
<iframe width="780" height="550" src="https://tbb.bio.uu.nl/bvd/simulations/australia/" title="Simulation"></iframe>
```


### Mermaid
  
Diagrams (Mermaid syntax):
  
```{mermaid}
%%| label: fig-variables
%%| fig-cap: "Types of models"
flowchart TB
A(Models) --> C("Analytical (mathematical)")
A --> B("Numerical (computational)")
B --> F(Individual-based model)
B --> G(Cellular automaton)
C --> E(Differential equation)
C --> D(MAPs)
```

Which can be referred to @fig-variables.

### Callouts

Call-outs can organise information and highlight important points.
  
::: callout-note
Note that there are five types of callouts, including: `note`,
`warning`, `important`, `tip`, and `caution`.
:::
  
::: callout-tip
## Tip with Title

This is an example of a callout with a title.
:::
  
::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by
the user. You can use `collapse="true"` to collapse it by default or
`collapse="false"` to make a collapsible callout that is expanded by
default.
:::
  
::: {#tip-example .callout-tip}
## Cross-Referencing a Tip
    
Add an ID starting with `#tip-` to reference a tip.
:::
      
See @tip-example...
    
### How to format questions/problem sets
    
::: {#exr-test1}
## Test 1
      
The equation of any straight line, called a linear equation, can be written as:
        
$$ 
y = mx + b
$$ {#eq-line}
      
Refer to the equation like this @eq-line or like [Customlabel @eq-line].
        
**a.** Blabla?
          
**b.** Of blablabla?
:::
          
### Sharing data tables:
          
```{r}
#| label: tab-anscombe
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| 

library(DT)
library(datasets)
datatable(anscombe, options = list(pageLength = 5))
```

